Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-21 size_differentiated_export.tex
Updates from Overleaf

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking. In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2016,Palevsky_2018}. We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of particle export flux closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

@@

%FIG6
\begin{figure}[ht]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded depth anomaly in the median particle depth 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model. [right]  Depth profile of the PDF of the number of particle for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_export}
\end{figure}

Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b). In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward flux within the first 15 days of the simulation. For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring in the presence of submesoscale dynamics. %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}

The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b). The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$). However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model, suggesting that the export for this sinking-velocity class remains mostly gravitationally-driven.

\begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}). Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
	\caption{PDF of biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom]. Inserts show the total downward biomass flux associated with each sinking-velocity class. Both winter dynamics and steeper June slope tend to increase the relative contribution of slower-sinking particles.}	
	\label{fig: biomass_export}
\end{figure}

As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics. Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes. The contribution from slow-sinking particles to the total biomass export flux expectedly decreases with the Junge slope. The decrease in biomass export flux is constant through time and can be predicted using Equation (\ref{eq: biomassjungeslope}):

\begin{equation}
    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
    %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
\end{equation}
Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively. %\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}

The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}). %While the particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

@@

 Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.

 %FIG7
 \begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
	\caption{Snapshot of the biomass PDF versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the total downward biomass flux associated with each sinking-velocity class. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}	
	\label{fig: biomass_export_remin}
\end{figure}

 The biomass export flux is also reduced compared to the case with no remineralization. In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases. In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export over different timescales (dash lines in Figure \ref{fig: biomass_export_remin}). Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by several orders of magnitude.

 In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}). The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported. As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

>>>>

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle downward flux, using Lagrangian particle-tracking. Downward particle flux is expected to be a combination of their sinking velocity and the vertical advective currents affecting the particle along its pathway. The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution}d for both summer and winter cases. In the summer, the PDF of particle density versus depth remains relatively narrow through time, and is centered on a depth level that can be predicted using a simple 1D gravitational model (see shaded curves in Figure \ref{fig: particle_depth_distribution}). PDFs of particle density also vary little among particles classes with different sinking velocities, suggesting that downward fluxes of particles is greatly dominated by gravitational settling and is not subject to significant vertical ocean currents.

%FIG6
\begin{figure}[ht!]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$. [right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.\fixme{Add a)-d) symbols} \fixme{smaller fontsize}}	
	\label{fig: particle_depth_distribution}
\end{figure}

In the winter, however, the PDF of particle density versus depth is wider, in agreement with the stronger vertical ocean currents occurring in the winter (see Figure \ref{fig: dynamics}). The deviation in the downward particle flux from the traditionally considered 1D gravitational model can be seen in Figure \ref{fig: particle_depth_distribution} (panels (a)-(c)). Slower-sinking particles deviate more than faster-sinking particles, exhibiting median depth anomalies up to 50 m. This is due to the fact that slower-sinking particles spend more time in the mixed layer, where most of the stronger vertical currents tend to occur (Figure \ref{fig: dynamics}). An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (where particles are shallower than expected) and negative (particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km). This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles and their associated .%, which is explicitly shown in Figure \ref{fig: biomass_export}.

A relative amount of biomass is associated to the particles using equation \ref{eq: biomassjungeslope}. The PDF of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}. Following the traditional paradigm derived from the simple 1D gravitational model, the downward flux of biomass in the summer is dominated by faster-sinking particle classes capable of carrying particulate material downwards more efficiently. The contribution of slower-sinking particles, however, critically depends on the slope of the size spectrum (see Figure \ref{fig: sinking_velocity_spectrum}). As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases. In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.1\% to 10\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$. While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles. This result can be explained by the fact that, in the summer, vertical velocities are weak and vertical biomass fluxes are therefore gravitationally-driven.

%FIG7
\begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}). Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom]. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class. Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.\fixme{bigger fontsize}}
	\label{fig: biomass_export}
\end{figure}

In the winter, the PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day. For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes. Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass. When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux. In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux.

 %In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2016,Palevsky_2018}. We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.

%The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of particle export flux closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

@@

%Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b). In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward flux within the first 15 days of the simulation. For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring in the presence of submesoscale dynamics. %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}

%The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b). The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$). However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model, suggesting that the export for this sinking-velocity class remains mostly gravitationally-driven.

%As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics. Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes. The contribution from slow-sinking particles to the total biomass export flux expectedly decreases with the Junge slope. The decrease in biomass export flux is constant through time and can be predicted using Equation (\ref{eq: biomassjungeslope}):

%\begin{equation}
%    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
    %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
%\end{equation}
%Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively. %\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}

%The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}). %While the particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

@@

 Both ocean dynamics at submeso-scales and the Junge slope were identified as key factors impacting the respective role played by different particle classes in driving downward biomass fluxes. Simple Lagrangian particles were used to isolate the effects of these two factors. In reality, however, sinking velocities of particulate matter varies in time as the particles slowly remineralize. A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation \ref{eq: sinking_velocity_remin}, to investigate the impact that remineralization processes have on our findings. The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over shorter timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes. While this paradigm holds for flatter Junge slope, where the biomass content is dominated by faster-sinking particles, it becomes inadequate at steeper slopes.

 Figure \ref{fig: biomass_export_remin} shows the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without remineralization processes. As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time \fixme{refer to Fig 9?}.

 During summertime and in the absence of remineralization, downward fluxes of biomass are dominated by faster-sinking particles, even for steeper Junge slope. This is due to the fact that the flux of biomass $\left<wB\right> = \left<w_sB\right> + \left<w_aB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content. This is characteristics of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes. Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize. This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where the PDFs of relative biomass per particle class are centered over lower vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}. As a result, the gravitationally-driven term $\left<w_sB\right>$ becomes small, and the downward flux of biomass is generally advectively-driven. The advectively-driven component of the biomass fluxes is uniform across particle classes, as it only depends on ocean currents. Thus, in a advectively-driven system where $\left<w_sB\right> << \left<w_aB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a). When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics. Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes.

 These results highlight the importance in considering slower-sinking particle classes when considering downward biomass fluxes. It also demonstrates that, contrarily to the traditional paradigm, remineralization processes enhance the role played by slower-sinking particles in biomass fluxes, in cases where the biomass spectrum slope is negative.

 The timescales over which the system transitioned from an gravitationally-driven to an advectively-driven system depends on the remineralization model used.

  %FIG8
 \begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}	
	\label{fig: biomass_export_remin}
\end{figure}

 \fixme{main points of new figure 8:
\begin{itemize}
    \item The impact of remineralization is three-fold: (1) it affects the total amount of biomass, as biomass is slowly remineralized - as illustrated by the decrease in area below the curves. (2) It shifts the PDFs of relative biomass as a function of vertical velocity towards slower vertical velocities. that is because, as they remineralize, the particles slow down. This has less of an impact on slower-sinking particles, as they are already sinking slowly anyway, so their PDFs don't change much, and the resulting downward biomass flux remains relatively large. faster-sinking particles, however, are more affected by the remineralization process, as their total vertical velocity shifts from gravitationally driven to advectively driven. as a result, their associated downward relative biomass flux is greatly decreased. Slow-sinking particles dominate the downward relative flux of biomass in both the summer and winter in the presence of remineralzation, as opposed to just the summer when remineralization is not included.
\end{itemize}
}

 %Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.

 %The biomass export flux is also reduced compared to the case with no remineralization. In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases. In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export over different timescales (dash lines in Figure \ref{fig: biomass_export_remin}). Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by several orders of magnitude.

 %In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}). The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported. As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.
